Adaptive Video Streaming with Optimized Bitstream Extraction and PID-based Quality Control

### 2016-03-22 tmm.tex
Revert "Final single column"
This reverts commit 2e8eebe0417dc7e6d06c5b277e405902af328261.
Final double column
Correct a bibitem
Proof

% Note that the a4paper option is mainly intended so that authors in
% countries using A4 can easily print to A4 and see how their papers will
% look in print - the typesetting of the document will not typically be
% affected with changes in paper size (but the bottom and side margins will).
% Use the testflow package mentioned above to verify correct handling of
% both paper sizes by the user's LaTeX system.
%
% Also note that the "draftcls" or "draftclsnofoot", not "draft", option 
% should be used if it is desired that the figures are to be displayed in
% draft mode.
%
\documentclass[journal,draftclsnofoot,onecolumn]{IEEEtran}
%\documentclass[journal]{IEEEtran}
%
% If IEEEtran.cls has not been installed into the LaTeX system files,
% manually specify the path to it like:
% \documentclass[journal]{../sty/IEEEtran}

@@

% author names and IEEE memberships
% note positions of commas and nonbreaking spaces ( ~ ) LaTeX will not break
% a structure at a ~ so this keeps an author's name from being broken across
% two lines.
% use \thanks{} to gain access to the first footnote area
% a separate \thanks must be used for each paragraph as LaTeX2e's \thanks
% was not built to handle multiple paragraphs
%
\author{Shengbin~Meng, Jun~Sun, {\em Member, IEEE}, Yizhou~Duan and Zongming~Guo, {\em Member, IEEE} % <-this % stops a space
\thanks{Manuscript received July 15, 2015; revised December 3, 2015 and January 12, 2016; accepted February 21, 2016. This work was supported by  National Key Technology R\&D Program of China under Grant 2015AA011605 and National Natural Science Foundation of China under contract No. 61271020.}
\thanks{Copyright (c) 2013 IEEE. Personal use of this material is permitted. However, permission to use this material for any other purposes must be obtained from the IEEE by sending a request to pubs-permissions@ieee.org.}
\thanks{The authors are with the Institute of Computer Science and Technology, Peking University, Beijing%
, 100080, China (email: mengshengbin@pku.edu.cn, sunjun@pku.edu.cn, duanyizhou@pku.edu.cn, guozongming@pku.edu.cn). Jun Sun and Zongming Guo are also with the Cooperative Medianet Innovation Center, Shanghai, 200240, China. Jun Sun is the corresponding author.}
}

@@

The state-of-the-art solutions for avoiding playback pause in the client media player mainly focus on how to select and schedule the video packets. In \cite{Gao06}, K. Gao et al. proposed a priority-based scheduling strategy, which guarantees that packets of higher importance will be transmitted earlier. Among the packets with the same priority, those with the earliest deadline will be transmitted first. A similar solution is proposed in \cite{Schierl10}, where the video data are pre-buffered in several buffers of different priorities. Whenever re-buffering occurs, the quality will be degraded to a lower level to meet the time and rate constraints. Although the priority-based scheduling strategies perform well in maintaining a non-paused video play, they do not take quality fluctuation into account. As a result, users may still suffer from the frequent fluctuation of video quality.

@@

We apply the above linear decoding feature to the case of quality scalability of SVC and obtain a Linear Error Model (LEM). According to (\ref{eq:linear}), for a bitstream just containing the base layer, we have:
\begin{equation}
\label{eq:base0}
s_{B} = {\rm\bf M} \cdot s_{B} + {\rm\bf T}_{B} \cdot c_{B} + p \: ,
\end{equation}
where the subscript $B$ indicates the base layer variables. In quality scalability, the enhancement is mainly the refinement of the transform coefficients. For a bitstream containing an enhancement packet set $I_1$, the reconstruction relationship can be expressed as:
\begin{equation}
\label{eq:subset1}
s_{I_1} = {\rm\bf M} \cdot s_{I_1} + {\rm\bf T}_{B} \cdot c_{B} + \Big( \sum_{i \in I_1}{\rm\bf T}_i \cdot c_i \Big) + p \: ,
\end{equation}
where $i$ refers to an enhancement packet in the set $I_1$, $c_i$ is a vector containing coefficients within the enhancement packet $i$, ${\rm\bf T_i}$ is the transform matrix depending on the QP value of $i$ and ${\rm\bf T}_i \cdot c_i$ gives the residual values decoded from $i$.

@@

\bibitem{Schierl10}
Y. Schierl, R. Sanchez, C. Globisch, Hellge, and T. Wiegand, ``Priority-based media delivery using SVC with RTP and HTTP streaming'', {\em Multimedia Tools And Applications}, vol. 55, no. 2, pp. 227-246, Sep. 2010.

>>>>

% Note that the a4paper option is mainly intended so that authors in
% countries using A4 can easily print to A4 and see how their papers will
% look in print - the typesetting of the document will not typically be
% affected with changes in paper size (but the bottom and side margins will).
% Use the testflow package mentioned above to verify correct handling of
% both paper sizes by the user's LaTeX system.
%
% Also note that the "draftcls" or "draftclsnofoot", not "draft", option 
% should be used if it is desired that the figures are to be displayed in
% draft mode.
%
%\documentclass[journal,draftclsnofoot,onecolumn]{IEEEtran}
\documentclass[journal]{IEEEtran}
%
% If IEEEtran.cls has not been installed into the LaTeX system files,
% manually specify the path to it like:
% \documentclass[journal]{../sty/IEEEtran}

@@

% author names and IEEE memberships
% note positions of commas and nonbreaking spaces ( ~ ) LaTeX will not break
% a structure at a ~ so this keeps an author's name from being broken across
% two lines.
% use \thanks{} to gain access to the first footnote area
% a separate \thanks must be used for each paragraph as LaTeX2e's \thanks
% was not built to handle multiple paragraphs
%
\author{Shengbin~Meng, Jun~Sun, {\em Member, IEEE}, Yizhou~Duan and Zongming~Guo, {\em Member, IEEE} % <-this % stops a space
\thanks{Manuscript received July 15, 2015; revised December 3, 2015 and January 12, 2016; accepted February 21, 2016. This work was supported by  National Key Technology R\&D Program of China under Grant 2015AA011605 and National Natural Science Foundation of China under contract No. 61271020.}
\thanks{Copyright (c) 2016 IEEE. Personal use of this material is permitted. However, permission to use this material for any other purposes must be obtained from the IEEE by sending a request to pubs-permissions@ieee.org.}
\thanks{The authors are with the Institute of Computer Science and Technology, Peking University, Beijing%
, 100080, China (email: mengshengbin@pku.edu.cn, sunjun@pku.edu.cn, duanyizhou@pku.edu.cn, guozongming@pku.edu.cn). Jun Sun and Zongming Guo are also with the Cooperative Medianet Innovation Center, Shanghai, 200240, China. Jun Sun is the corresponding author.}
}

@@

The state-of-the-art solutions for avoiding playback pause in the client media player mainly focus on how to select and schedule the video packets. In \cite{Gao06}, Gao et al. proposed a priority-based scheduling strategy, which guarantees that packets of higher importance will be transmitted earlier. Among the packets with the same priority, those with the earliest deadline will be transmitted first. A similar solution is proposed in \cite{Schierl10}, where the video data are pre-buffered in several buffers of different priorities. Whenever re-buffering occurs, the quality will be degraded to a lower level to meet the time and rate constraints. Although the priority-based scheduling strategies perform well in maintaining a non-paused video play, they do not take quality fluctuation into account. As a result, users may still suffer from the frequent fluctuation of video quality.

@@

We apply the above linear decoding feature to the case of quality scalability of SVC and obtain a Linear Error Model (LEM). According to (\ref{eq:linear}), for a bitstream just containing the base layer, we have:
\begin{equation}
\label{eq:base0}
s_{B} = {\rm\bf M} \cdot s_{B} + {\rm\bf T}_{B} \cdot c_{B} + p \: ,
\end{equation}
where the subscript $B$ indicates the base layer variables. In quality scalability, the enhancement is mainly the refinement of the transform coefficients. For a bitstream containing an enhancement packet set $I_1$, the reconstruction relationship can be expressed as:
\begin{equation}
\label{eq:subset1}
s_{I_1} = {\rm\bf M} \cdot s_{I_1} + {\rm\bf T}_{B} \cdot c_{B} + \Big( \sum_{i \in I_1}{\rm\bf T}_i \cdot c_i \Big) + p \: ,
\end{equation}
where $i$ refers to an enhancement packet in the set $I_1$, $c_i$ is a vector containing coefficients within the enhancement packet $i$, ${\rm\bf T}_i$ is the transform matrix depending on the QP value of $i$ and ${\rm\bf T}_i \cdot c_i$ gives the residual values decoded from $i$.

@@

\bibitem{Schierl10}
T. Schierl, Y.S. De La Fuente, R. Globisch, C. Hellge and T. Wiegand, ``Priority-based media delivery using SVC with RTP and HTTP streaming'', {\em Multimedia Tools And Applications}, vol. 55, no. 2, pp. 227-246, Sep. 2010.
